When are Fuzzy Extractors Possible?

### 2014-10-02 trunk/info-bounds/FuzzyExtPossibility.tex
minor notes in the intro

\def\shownotes{0}
\def\blinded{0}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

@@

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Repeatable entropy sources enable applications cryptographic applications such as authentication and key agreement\bnote{more?}.  However, many entropic sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources it is often necessary to remove noise, and achieve the same value in subsequent readings.  \bnote{I tried to remove entropy from this but it needs to be cleaned up}

Bennett, Brassard, and Roberts~\cite{bennett1988privacy} introduced this problem in the interactive setting. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

@@

@@

@@

@@

@@

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.

@@

\section{Proof of \thref{thm:imposs fuzz ext}}
\label{sec:fuzz ext proof}
\begin{proposition} 
\label{prop:dist fuzzy ent fuzz}
For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some fixed $W\in\mathcal{V}$.  The value $w_{1,..., \nu}$ is uniform, so $\Hoo(W) =\omega(\log n)$.  Recall that $t=o (n/\nu)$.  We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Denote by $x, x'$ the values that produce $w, w'$ respectively.  Clearly, $x\neq x'$.  Thus, for any $i$, $a_i w_1 + b_i \neq a_i x' + b_i$.  This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$ and thus $\dis(w, w') \ge n/\nu$.  Thus, $\Hfuzz(W) = \Hoo(W)= \omega(\log n)$.
\end{proof}

>>>>

\def\shownotes{1}
\def\blinded{0}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

@@

\newpage
\tableofcontents\newpage

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Sources of secret random bits are necessary for most cryptographic applications.  In many situations, these bits are not explicitly and reliably stored for future use, but are reproduced as a result of some process (such as reading a biometric or a physically unclonable function).
However, many such sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources it is often necessary to remove noise, and achieve the same value in subsequent readings.  \bnote{I tried to remove entropy from this but it needs to be cleaned up}

Bennett, Brassard, and Robert~\cite{bennett1988privacy} introduced this problem in the interactive setting. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

@@

\anote{Suggested title: "Fuzzy Minentropy"}

@@

\anote{Suggested title: "Characterization  for Distribution-aware Extractability". Emphasize if we know the distribution on $W$}

@@

\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors". Also, "typically fuzzy extractors cannot be tailored". Also "for a family of sources" $\to$ "to a family of sources".}

@@

\anote{Suggested title: "Results on Information Reconciliation (Secure Sketches)"}

@@

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.

@@

\section{Proof of \thref{thm:imposs fuzz ext}}
\label{sec:fuzz ext proof}
\begin{proposition} 
\label{prop:dist fuzzy ent fuzz}
For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some fixed $W\in\mathcal{V}$.  The bits $w_{1,..., \nu}$ are uniform, so $\Hoo(W) =\omega(\log n)$.  Recall that $t=o (n/\nu)$.  We now show that for any $w, w'\in W$, $\dis(w, w') \ge n/\nu$ and thus $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Denote by $x, x'$ the values that produce $w, w'$ respectively.  Clearly, $x\neq x'$.  Thus, for any $i$, $a_i x + b_i \neq a_i x' + b_i$.  This implies that $w_{i\nu+1,...., (i+1)\nu} \neq w'_{i\nu+1,..., (i+1)\nu}$. That is, at least one of the bits in each block differs between $w$ and $w'$, and so $\dis(w, w') \ge n/\nu$. Since no two values in the support of $W$ lie in the same ball of radius $t$, we have $\Hfuzz(W) = \Hoo(W)= \omega(\log n)$.
\end{proof}
